---
title: "Data Visualisation GGPlot2"
author: "Emmanuel Akinbode"
date: "10/30/2019"
output: html_document
---

```{r}
library(ggplot2)
```

```{r}
dmd<- read.table("data/diamond.csv", header=T, dec=".", sep=",")
head(dmd)[1:5]
```

```{r}
ggplot(dmd, aes(x=carat, y=price))
```

## adding scatter point var: 2 continous
```{r}
ggplot(dmd, aes(x=carat, y=price)) + geom_point(colour="blue")
```

```{r}
ggplot(dmd, aes(x=carat, y=price, colour=cut)) + geom_point()
```


## Bar graph(geom_bar) var: 1 categorica, Histogram(geom_hist) var: 1 continous, ##Boxplot(geom_boxplot) var: 1 cat + cont, Jitter(geom_jitter) var: 1 cat + cont


```{r}
library(readxl)
library(tidyverse)
dta<-read_excel("data/mbta.xlsx", skip = 1, range = cell_cols(2:60))
view(dta)
```

##Gathering the years
\footnotesize

The _gather_ function in _tidyr_ packege helps in gathering multiple columns and collapse the column into key_value pairs as seen below
\footnotsize


```{r}
dta_tidy1 <- dta %>% gather(`2007-01`: `2011-10`, key = "year", value = "passengers")
dta_tidy1
```

```{r}
dta_tidy2 <- dta_tidy %>% separate(year, into = c("year", "month"))
dta_tidy2
```


```{r}
dt<-dta_tidy2 %>% filter(mode %in% c ("Commuter Rail", "Heavy Rail","Light Rail","Private Bus"))
dt
```

##Spreading mode of transportation

\foornotesize
The _spread_ function helps in spreading a key-value pair across multiple columns
\footnotesize

```{r}
dta_tidy3 <- dta_tidy2 %>% spread(mode, passengers)
dta_tidy3
```

```{r}
dta_tidy4 <- dta_tidy3 %>% .[,c(1:2,6:8,10)]
dta_tidy4
```


```{r}
dta_tidy5<- dta_tidy4 %>% gather(`Commuter Rail`:`Private Bus`, key="rail_type", value="passengers")
dta_tidy5
```


```{r}
ggplot(dta_tidy5, aes(x=year, y=passengers, colour = rail_type, size = rail_type, shape = rail_type )) + geom_point() + ggtitle("Passengers against Year based on Rail_Type") + ylab("Numbers of Passengers") + xlab("Years")
```

```{r}
glimpse(dta_tidy5)
```

```{r}
dta_tidy5$year<-as.factor(dta_tidy5$year)
dta_tidy5$rail_type<-as.factor(dta_tidy5$rail_type)
dta_tidy5$passengers<-as.numeric(dta_tidy5$passengers)
glimpse(dta_tidy5)
```


##Rather tha using ggtitle, labs can be used.
```{r}
ggplot(dta_tidy5, aes(x=year, y=passengers, colour = rail_type, size = rail_type, shape = rail_type )) + geom_point() + labs(title ="Passengers against Year based on Rail_Type", ylab="Numbers of Passengers", xlab= "Years")
```

##Back to Diamond file. Setting Axis limits

```{r}
p2<- ggplot(dmd, aes(x=carat, y=price)) + geom_point(aes(color=color, shape=cut, size=0.05)) + labs(title = "Relationship between Price and Carat of Diamond") + scale_y_continuous(name="Price", limits = c(0,15000), breaks = seq(0,15000, by=3000)) + scale_x_continuous(name="Carat", limits = c(0,4), breaks = seq(0,4, by=0.5)) + scale_color_brewer(name = "Diamond Color", palette = "Set1")
suppressWarnings(print(p2))

```

```{r}
glimpse(dt)
```

```{r}
dt$mode<-as.factor(dt$mode)
dt$year<-as.factor(dt$year)
dt$passengers<-as.numeric(dt$passengers)
glimpse(dt)
```

```{r}
var<-ggplot(dt, aes(x=year, y=passengers, color=mode)) + geom_point() + labs(title = "Number of Passengers Across the Years based on the Mode", x="Years", y="Number of passengers") + theme_grey()
var
```

```{r}
var1<-ggplot(dt, aes(x=year, y=passengers)) + geom_point() + labs(title = "Number of Passengers Across the Years based on the Mode", x="Years", y="Number of passengers") + theme_grey() + facet_grid(~mode)
var1
```

```{r}
p8<- ggplot(dmd, aes(x=carat, y=price)) + geom_point(aes(color=cut, shape=cut, size=0.05)) + geom_smooth(method="lm") + labs(title="Relationship between Price and Carat of Diamond") + scale_y_continuous(name="Price", limits= c(0,15000), breaks = seq(0, 15000, by = 3000)) + scale_x_continuous(name="Carat", limits = c(0,4), breaks = seq(0,4, by = 0.5)) + scale_color_manual(name = "Diamond Cut", values = c("blue", "orange", "red", "purple", "cyan"), labels = c("Fair","Good","Ideal","Premium","VG")) + facet_grid(~cut) + theme_bw()
p8
```

```{r}
ggplot(dmd, aes(x = cut)) + geom_bar()
```

```{r}
ggplot(dmd, aes(x = cut, fill=color)) + geom_bar()
```

```{r}
ggplot(dmd, aes(x = cut, fill=color)) + geom_bar(position = "dodge")
```

```{r}
ggplot(dmd, aes(x = cut, fill=color)) + geom_bar(position = "dodge") + coord_flip()
```

```{r}
ggplot(dt, aes(y = passengers, x = mode)) + geom_boxplot()
```

```{r}
ggplot(dmd, aes(y = price, x=cut, fill = color )) + geom_boxplot() + labs(title="Relationship between Price and Carat of Diamond") + scale_y_continuous(name="Price", limits= c(0,15000), breaks = seq(0, 15000, by = 3000)) + theme(axis.text.x = element_text(face="bold", color="#993333", size=14, angle=45))
```

```{r}
ggplot(dmd, aes(y=price, x=cut)) + geom_jitter(height = 0, width = 0.3)
```

```{r}
ggplot(dmd, aes(y=price, x=cut)) + geom_jitter() + facet_grid(~color) 
```

```{r}
ggplot(dmd, aes(y = price, x = cut)) + geom_jitter(color = "orange") + geom_boxplot(fill = NA, color = "black")
```

```{r}
ggplot(dmd, aes(x = price)) + geom_histogram(color = "blue")+ labs(title = "Histogram of Price", x="Price",y="Frequency")+ facet_grid(~color)
```

```{r}
ggplot(dmd, aes(x = price)) + geom_density(fill = "red")+ labs(title = "Histogram of Price", x="Price",y="Frequency")+ facet_grid(color~.)
```

```{r}
library(hflights)
glimpse(hflights)
```

```{r}
dt<- data("hflights")
glimpse(dt)
```

```{r}
str(iris)

```

```{r}
dt<-(iris)
str(dt)
glimpse(dt)
```

```{r}
iris
```
```{r}
flower<- ggplot(iris, aes(x=Sepal.Width, y=Sepal.Length)) + geom_point(aes(color=Species)) + labs(title="Plot of Sepal width against Sepal length") + scale_y_continuous(name="Sepal Length") + scale_x_continuous(name="Sepal Width") 
flower
```

```{r}
flower<- ggplot(iris, aes(x=Species, y=Sepal.Length)) + geom_boxplot() 
flower
```

#price y, bathroom x, facet based status. y is always the response
```{r}
h<- read.csv(file.choose(), header = T)
glimpse(h)
```

```{r}
h1<-ggplot(h, aes(x= Bathrooms, y= Price)) + geom_point() + labs(title="Price of Bathrooms") + scale_y_continuous(name="Price") + scale_x_continuous(name="Bathrooms") + facet_grid(~Status)
h1
```
