---
title: "Inferential Statistics"
author: "Emmanuel Akinbode"
date: "10/30/2019"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r}
dt<-read.csv("data/diamond.csv", header=T)
t.test(dt$price,mu=3000)
```

```{r}
ct<-read.csv(file.choose(), header=T)
t.test(ct$area_se~ct$diagnosis, alternative="two.sided")
ct
```

```{r}
x<-c(239, 170, 182, 143, 141, 170, 160, 154, 185, 130)
y<-c(362,343, 330, 340, 314, 567, 292, 439, 312, 2920)
paired_1<-t.test(x,y, paired=TRUE)
paired_1
```

#Exercise

#1.
# Ho: mu = 0.4
# H1: mu > 0.4
# Level of significance : 0.05


```{r}
dt<-read.csv("data/diamond.csv", header=T)
t.test(dt$carat,mu=0.4, alternative = "greater")
```
#Conclusion:
# We reject Ho because our p-value is less than our level of significance, our mean is greater than 0.4



#Question 2
#1.
# Ho: Um = Ub
# H1: Um != Ub
# Level of significance : 0.05

```{r}
cev<-read.csv(file.choose(), header=T)
t.test(cev$area_worst~cev$diagnosis, alternative="two.sided")
```
#Conclusion:
We reject Ho because our p-value is less than our level of significance and it shows a difference between the mean of area_worst and diagnosis.



#Question 3
Ho: Before = After
H1: Before != After
Level of Significance: 0.05

```{r}
before<-c(80,45,78,89,80,90,91,89,56,78,89,81)
after<-c(61,71,62,78,88,71,78,79,67,66,78,79)
tumor<-t.test(before, after, paired = TRUE)
tumor
```
Conclusion: We accept Ho because our p-value is greater than our level of significance, showing there is no difference before and after the tumor