title: "Test"
author: "Emmanuel Akinbode"
date: "10/18/2019"
output:
  pdf_document: default
  html_document: default
cohort: Cohort 1
---

##Question 1. Write R program to create a matrix taking a given vector of numbers as input. Display the matrix

```{r}
Ques1 <- matrix(1:9, nrow = 3, ncol = 3, byrow = TRUE)
Ques1

```

##Question2. Write R program to create “two” 2x3 matrix and add, subtract, multiply the matrices. 
```{r}
mat1 <- matrix(1:6, nrow=2, ncol = 3, byrow = TRUE)
mat2 <- matrix(7:12, nrow = 2, ncol = 3, byrow = TRUE)

add<- mat1 + mat2
sub<- mat2 - mat1
mult<- mat1 * mat2
mat1
mat2
add
sub
mult
```

##Question 3: Write R program to access the element at 3rd column and 2nd row of a given matrix.
```{r}
access_mat1<- mat1[2,3]
access_mat2<- mat2[2,3]
access_mat1
access_mat2

```

##Question 4: Write R program to create vector of numeric, complex, logical and character types of length 

```{r}
number<- c(1:6)
numeric_vector<- as.numeric(number)
complex_vector<-as.complex(number)
logical_vector<-as.logical(number)
char_vector<-as.character(number)

numeric_vector
complex_vector
logical_vector
char_vector

```

##Question 5: Write R program to multiply two vectors of integer type of length 3
```{r}
int1 <- 1:3
int2 <- 4:6
vect <- int1 * int2
vect
```

##Question 6: Load the Tumor data set into R using the read.table() function.

```{r}
tumor<- read.table(file.choose(), header = T, sep = "\t")
View(tumor)
tumor
```


Question 7: Using the data in Q6, Plot the scatter plot of the variables “time”  and “futime “, with "time" on the y-axis and "futime" on the x-axis.  Format your plot by putting title on the plot.

```{r}

plot(tumor$futime, tumor$time, main="Relationship between Futime and Time",xlab="futime", ylab="time")
```

#3Question 8:  Using the data in Q6, Carry out histogram plot of the “time” variable and Title you plot
```{r}
hist(tumor$time,  main="Histogram showing time", ylab="time")
```